\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\title{BlocTime: Simple Guide for Everyone}
\author{BlocTime Development Team}
\date{\today}

\begin{document}

\maketitle

\section{What is BlocTime?}

BlocTime is like a digital savings account that rewards you for locking up your tokens. The longer you lock them, the more bonus tokens you earn!

\section{How Does It Work?}

\subsection{Staking (Locking Your Tokens)}
\begin{itemize}
\item You deposit your tokens into BlocTime
\item Choose how long to lock them (measured in blocks)
\item Get BlocTime tokens as a reward
\item \textbf{The longer you lock = The more you earn!}
\end{itemize}

\textbf{Example:} Lock 100 tokens for 1000 blocks, get 120 BlocTime tokens. Lock for 5000 blocks, get 200 BlocTime tokens!

\subsection{The Marketplace}
\begin{itemize}
\item Buy stable tokens using approved cryptocurrencies
\item Prices are set fairly using trusted sources
\item Simple credit/debit system
\item Your stable tokens are always worth the same
\end{itemize}

\textbf{Example:} Pay with ETH to get stable tokens you can use anywhere in the system.

\subsection{The Treasury (Shared Vault)}
\begin{itemize}
\item Hold BlocTime tokens = Own part of the treasury
\item Treasury collects different types of tokens
\item Claim your share anytime
\item \textbf{Own 10\% of BlocTime tokens = Get 10\% of ALL treasury tokens!}
\end{itemize}

\textbf{Example:} Treasury has ETH, USDC, and DAI. You own 5\% of BlocTime tokens, so you can claim 5\% of each token type!

\subsection{The Registry (Digital Catalog)}
\begin{itemize}
\item Register your digital assets
\item Store information about them
\item Transfer ownership easily
\item Keep track of everything you own
\end{itemize}

\textbf{Example:} Register your NFT collection, game items, or any digital asset with metadata.

\subsection{Permissions (Access Control)}
\begin{itemize}
\item Create keys that control access
\item Give different permissions to different people
\item Manage who can do what
\item Keep your assets secure
\end{itemize}

\textbf{Example:} Create a master key for your project, then give team members specific access keys.

\section{Why Use BlocTime?}

\begin{itemize}[label=\checkmark]
\item \textbf{Earn Rewards} - Get paid for holding tokens longer
\item \textbf{Fair Distribution} - Everyone gets their fair share based on ownership
\item \textbf{Multiple Tokens} - Work with many different cryptocurrencies
\item \textbf{Secure} - Built with industry-standard security
\item \textbf{Transparent} - Everything happens on the blockchain
\item \textbf{Flexible} - Use just the parts you need
\end{itemize}

\section{Simple Use Cases}

\subsection{For Investors}
\begin{enumerate}
\item Stake tokens for rewards
\item Earn BlocTime tokens
\item Claim treasury distributions
\item Profit! \textcolor{green}{\$\$\$}
\end{enumerate}

\subsection{For Projects}
\begin{enumerate}
\item Create a treasury for your community
\item Let token holders share in profits
\item Build trust and loyalty
\item Grow together! \textcolor{blue}{$\uparrow$}
\end{enumerate}

\subsection{For Traders}
\begin{enumerate}
\item Use the marketplace for stable tokens
\item Trade with confidence
\item Access multiple token types
\item Stay liquid! \textcolor{cyan}{$\sim$}
\end{enumerate}

\section{Key Benefits}

\subsection{Security First}
\begin{itemize}
\item Protected against common attacks
\item Audited code patterns
\item Safe token transfers
\end{itemize}

\subsection{Gas Efficient}
\begin{itemize}
\item Optimized for low fees
\item Batch operations available
\item Smart storage usage
\end{itemize}

\subsection{User Friendly}
\begin{itemize}
\item Simple interfaces
\item Clear documentation
\item Easy integration
\end{itemize}

\subsection{Decentralized}
\begin{itemize}
\item No single point of control
\item Community governed
\item Transparent operations
\end{itemize}

\section{Getting Started}

\begin{enumerate}
\item \textbf{Get Some Tokens} - Acquire the native token
\item \textbf{Connect Wallet} - Use MetaMask or similar
\item \textbf{Choose Action} - Stake, trade, or claim
\item \textbf{Confirm Transaction} - Approve in your wallet
\item \textbf{Done!} - Watch your rewards grow
\end{enumerate}

\section{Important Terms (Simple)}

\begin{itemize}
\item \textbf{Block}: A unit of time on the blockchain ($\sim$15 seconds)
\item \textbf{Staking}: Locking tokens to earn rewards
\item \textbf{Multiplier}: Bonus percentage for longer locks
\item \textbf{Treasury}: Shared vault of tokens
\item \textbf{Governance Token}: Token that gives you voting/claiming rights
\item \textbf{Oracle}: Trusted price information source
\end{itemize}

\section{Safety Tips}

\begin{itemize}
\item[\textcolor{red}{$\triangle$}] \textbf{Only invest what you can afford to lose}
\item[\textcolor{red}{$\triangle$}] \textbf{Longer locks = Can't withdraw early}
\item[\textcolor{red}{$\triangle$}] \textbf{Always verify contract addresses}
\item[\textcolor{red}{$\triangle$}] \textbf{Keep your wallet secure}
\item[\textcolor{red}{$\triangle$}] \textbf{Understand the risks}
\end{itemize}

\section{Questions?}

\begin{itemize}
\item Check the technical paper for details
\item Join the community Discord
\item Read the documentation
\item Ask in the forums
\end{itemize}

\section{Summary}

BlocTime makes it easy to:
\begin{itemize}
\item Earn rewards by staking
\item Share in treasury profits
\item Trade stable tokens
\item Register digital assets
\item Manage permissions
\end{itemize}

All in one simple, secure protocol!

\vspace{1cm}
\hrule
\vspace{0.5cm}

\textbf{Remember}: This is a simplified explanation. For technical details, security information, and complete specifications, please read the Technical Whitepaper.

\textbf{Start small, learn as you go, and welcome to BlocTime!}

\end{document}