\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{amsmath}

% Colors
\definecolor{maincolor}{RGB}{255,140,0}
\definecolor{accentcolor}{RGB}{0,191,255}

\title{\Huge\textbf{\textcolor{maincolor}{BlocTime}}\\[0.3cm]\Large Simple Guide for Everyone}
\author{}
\date{}

\begin{document}

\maketitle

\section*{\textcolor{maincolor}{What is BlocTime?}}

BlocTime is like a \textbf{digital savings account} that rewards you for locking up your tokens. The longer you lock them, the more bonus tokens you earn!

\vspace{0.5cm}

\section*{\textcolor{maincolor}{How Does It Work?}}

\subsection*{\textcolor{accentcolor}{1. Staking (Locking Your Tokens)}}

\begin{itemize}
    \item Deposit your tokens into BlocTime
    \item Choose how long to lock them (measured in blocks)
    \item Get BlocTime tokens as a reward
    \item \textbf{The longer you lock = The more you earn!}
\end{itemize}

\textbf{Example:} Lock 100 tokens for 1000 blocks → get 120 BlocTime tokens. Lock for 5000 blocks → get 200 BlocTime tokens!

\subsection*{\textcolor{accentcolor}{2. The Treasury (Shared Vault)}}

\begin{itemize}
    \item Hold BlocTime tokens = Own part of the treasury
    \item Treasury collects different types of tokens
    \item Claim your share anytime
    \item \textbf{Own 10\% of BlocTime tokens = Get 10\% of ALL treasury tokens!}
\end{itemize}

\subsection*{\textcolor{accentcolor}{3. The Marketplace}}

\begin{itemize}
    \item Buy stable tokens using approved cryptocurrencies
    \item Prices are set fairly using trusted sources
    \item Simple credit/debit system
    \item Your stable tokens are always worth the same
\end{itemize}

\vspace{0.5cm}

\section*{\textcolor{maincolor}{Why Use BlocTime?}}

\begin{center}
\begin{tikzpicture}
    \node[draw, fill=maincolor!20, rounded corners, text width=0.45\textwidth, align=center] at (0,0) {\textbf{Earn Rewards}\\Get paid for holding tokens longer};
    \node[draw, fill=accentcolor!20, rounded corners, text width=0.45\textwidth, align=center] at (8,0) {\textbf{Fair Distribution}\\Everyone gets their fair share};
    \node[draw, fill=maincolor!20, rounded corners, text width=0.45\textwidth, align=center] at (0,-2) {\textbf{Secure}\\Built with industry-standard security};
    \node[draw, fill=accentcolor!20, rounded corners, text width=0.45\textwidth, align=center] at (8,-2) {\textbf{Transparent}\\Everything happens on the blockchain};
\end{tikzpicture}
\end{center}

\vspace{0.5cm}

\section*{\textcolor{maincolor}{Simple Use Cases}}

\subsection*{For Investors}
\begin{enumerate}
    \item Stake tokens for rewards
    \item Earn BlocTime tokens
    \item Claim treasury distributions
    \item Profit! 💰
\end{enumerate}

\subsection*{For Projects}
\begin{enumerate}
    \item Create a treasury for your community
    \item Let token holders share in profits
    \item Build trust and loyalty
    \item Grow together! 🚀
\end{enumerate}

\vspace{0.5cm}

\section*{\textcolor{maincolor}{Getting Started}}

\begin{enumerate}
    \item \textbf{Get Some Tokens} - Acquire the native token
    \item \textbf{Connect Wallet} - Use MetaMask or similar
    \item \textbf{Choose Action} - Stake, trade, or claim
    \item \textbf{Confirm Transaction} - Approve in your wallet
    \item \textbf{Done!} - Watch your rewards grow
\end{enumerate}

\vspace{0.5cm}

\section*{\textcolor{maincolor}{Important Terms (Simple)}}

\begin{itemize}
    \item \textbf{Block}: A unit of time on the blockchain (~15 seconds)
    \item \textbf{Staking}: Locking tokens to earn rewards
    \item \textbf{Multiplier}: Bonus percentage for longer locks
    \item \textbf{Treasury}: Shared vault of tokens
    \item \textbf{Governance Token}: Token that gives you voting/claiming rights
\end{itemize}

\vspace{0.5cm}

\section*{\textcolor{red}{Safety Tips}}

\begin{itemize}
    \item[$\triangleright$] Only invest what you can afford to lose
    \item[$\triangleright$] Longer locks = Can't withdraw early
    \item[$\triangleright$] Always verify contract addresses
    \item[$\triangleright$] Keep your wallet secure
    \item[$\triangleright$] Understand the risks
\end{itemize}

\vspace{0.5cm}

\section*{\textcolor{maincolor}{Summary}}

BlocTime makes it easy to:
\begin{itemize}
    \item ✨ Earn rewards by staking
    \item 💎 Share in treasury profits
    \item 🔄 Trade stable tokens
    \item 🔐 Manage permissions
\end{itemize}

\textbf{All in one simple, secure protocol!}

\vspace{1cm}

\begin{center}
\textit{\textcolor{gray}{For technical details, security information, and complete specifications, please read the Technical Whitepaper.}}

\vspace{0.5cm}

\textbf{\textcolor{maincolor}{Start small, learn as you go, and welcome to BlocTime!}} 🎉
\end{center}

\end{document}